Portal Forecast

### 2017-05-04 portal-forecast.Rmd

```{r speciesforecasts, echo=FALSE, message=FALSE, warning=FALSE}
source("forecast_tools.R")
source("actual_census_counts.R")

data = compile_forecasts()
ensemble = dplyr::filter(data, level == 'All', model == 'Ensemble', date == max(date))
sp_predictions = get_sp_predicts(ensemble, 'All', lead_time = 1)
plot_data(sp_predictions, 'All')
```
```{r highabund_ts_forecasts, echo=FALSE, message=FALSE, warning=FALSE}
most_abund_sp = sp_predictions %>% 
  filter(species != 'total') %>% 
  arrange(desc(estimate)) %>% 
  head(3) %>% 
  select(species)

>>>>

```{r speciesforecasts, echo=FALSE, message=FALSE, warning=FALSE}
source("forecast_tools.R")

data = compile_forecasts()
ensemble = dplyr::filter(data, level == 'All', model == 'Ensemble', date == max(date))
sp_predictions = get_sp_predicts(ensemble, 'All', lead_time = 1)
plot_data(sp_predictions)
```
```{r highabund_ts_forecasts, echo=FALSE, message=FALSE, warning=FALSE}
most_abund_sp = sp_predictions %>% 
  filter(species != 'total') %>% 
  arrange(desc(estimate)) %>% 
  head(3) %>% 
  select(species)
